Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-10-18 paper/coverletter/rsos_response.tex
ready to resubmit!

          \revised{Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary. Student reports contained a section listing changes from the original. In response to a reviewer, we attempted to code studies using the classification scheme from LeBel et al. (2018).

@@

          	Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.}

@@

         \revised{The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).
         }

@@

          Psych Science makes up 45\% of the sample, so we felt we couldn't use journal as a predictor, since other journals are much much less represented. (I guess we could have done Psych Science versus everything else, but that wouldn't have been interpretable.)

          But, for your edification, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.

>>>>

          \revised{
          	Replications varied in how close they were to the original; while the goal was to replicate the original as closely as possible, some deviations were sometimes necessary. Student reports contained a section listing changes from the original. In response to a reviewer, we attempted to code studies using the classification scheme from (LeBel et al 2018).

@@

          	Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated. We did not consider these as reducing the degree of closeness.

          	}

@@

         \revised{The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73). As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.
         }

@@

          Psych Science makes up 45\% of the sample, so we felt we couldn't use journal as a predictor, since other journals are much much less represented.

          But, since you are interested, we did run the descriptive summary and the bivariate correlates on the Psych Science subsample.

### 2023-10-18 paper/manuscript.Rmd
ready to resubmit!

Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we can interpret as an overall subjective replication rate. `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications had outcomes with point-estimates within the prediction interval of the original outcome. The median *p*-original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. The subjective replication scores were moderately correlated with both prediction interval (r=`r round(sub_pred,2)`) and *p*-original (r=`r round(sub_p, 2)`) values; prediction interval and *p*-original were highly correlated with each other (r=`r round(pred_p,2)`).

@@

Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e. from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated. 
Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

>>>>

Across the 176 studies, the average subjective replication score was `r round(pluck(sub_rep_rate,1))`%, which we can interpret as an overall subjective replication rate. `r round(pluck(pred_int_rate,1))`% (`r predIntcount`/`r predInttotal`) of replications had outcomes with point-estimates within the prediction interval of the original outcome. The median *p*-original value on the original and replication point-estimates coming from the same distribution was `r round(pluck(porig_rate, 1),2)`, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. The subjective replication scores were moderately correlated with both prediction interval (r=`r round(sub_pred,2)`) and *p*-original (r=`r round(sub_p, 2)`) values; prediction interval and *p*-original were highly correlated with each other (r=`r round(pred_p,2)`). As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.

@@

Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated. We did not consider these as reducing the degree of closeness.

Four of the replication projects were included in RP:P, and 10 were previously reported in @hawkins2018 (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

### 2023-10-18 paper/manuscript.tex
ready to resubmit!

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 45\% (61/136) of replications had outcomes with point-estimates within the prediction interval of the original outcome. The median \emph{p}-original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73).

@@

Other common changes (that we did not consider as decreasing the closeness) were switching which convenience population was used (i.e.~from college students to crowdworkers or from one crowdwork platform to another), changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all), and removing secondary measures that were not part of the analyses being replicated.
Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{37}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).

>>>>

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 45\% (61/136) of replications had outcomes with point-estimates within the prediction interval of the original outcome. The median \emph{p}-original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. The subjective replication scores were moderately correlated with both prediction interval (r=0.36) and \emph{p}-original (r=0.27) values; prediction interval and \emph{p}-original were highly correlated with each other (r=0.73). As mentioned above, inconsistency between the subjective replication and numeric outcomes can occur in a few circumstances such as when there is a large precise original effect and a smaller, but clear replication effect; when there is a small, imprecise original effect and a smaller, null, or opposite replication effect; or when the key measure does not represent the overall pattern of the results.

@@

Other common changes were changing or reducing demographic surveys (which were used only in exploratory or secondary analyses, if at all) and removing secondary measures that were not part of the analyses being replicated. We did not consider these as reducing the degree of closeness.

Four of the replication projects were included in RP:P, and 10 were previously reported in (\protect\hyperlink{ref-hawkins2018}{37}) (which reported 11 student replications from the 2015-2016 class; one of those was excluded from the current sample for being non-experimental).
